Spatial Reasoning and Statistical Graphics

### 2014-10-19 Paper/Draft1/TestingVisualAptitude.Rnw
clarify appendix form

Participants will complete the following tasks (sample pictures included, full stimuli set will be added to the appendix once testing is complete). Tasks are designed so that participants are under time pressure; they are not expected to complete all of the problems in each section. This provides more discrimination between high scorers and prevents score compression at the top of the range. 

>>>>

Participants will complete the following tasks (sample pictures included, full stimuli set will be added to the appendix once we are sure there is no need for follow-up experiments). Tasks are designed so that participants are under time pressure; they are not expected to complete all of the problems in each section. This provides more discrimination between high scorers and prevents score compression at the top of the range. 
